INTELLIGENT SYSTEMS

### 2021-04-03 paper_4.tex
finish 4.4.1

>>>>

\subsection{EXPERIMENTAL RESULTS}
\subsubsection{Evaluation of Unsupervised Baseline Methods}
In summary, in order to have the effect of the camera-independecy on a 
set of images from different cameras, it is enough to be able to calculate 
the constancy of the color which, in other words, means having to detect the 
chromaticity of the illuminate that precisely illuminates the scene. Given the 
chromaticity estimated by the algorithm ($ p^{Est} $) and the effective chromaticity 
(white point or ground truth) ($ p^E $), the performance of an algorithm can be 
evaluated based on the result returned by the recovery angular error (RAE):
\begin{equation}
    RAE=\cos^{-1}\left(\frac{p^Ep^{Est}}{||p^E||~||p^{Est}||}\right)
\end{equation}
This error index is calculated both on the performances obtained in high 
resolution images and in those obtained at low resolution. To make some 
comparison, an algorithm that has a low RAE is the unsupervised algorithm 
GW \cite{0807099104} which assumes that the average chromaticity in an image is gray. 
Even the MaxRGB algorithm \cite{0807099103} manages to have good performance 
in images where there are saturated areas where, thanks to these, the white 
point can be easily recovered. MaxRGB is currently the only algorithm that 
manages to have a low RAE even with low quality images (1080p). The 
performances of these algorithms, together with two others (SoG and GE), 
are compared in figure \ref{fig:RAE} where for each set of images (Lab 
Printouts, Lab Real Scenes, $ 1^{st} $ Field Set and $ 2^{nd} $ Field set), taken from different cameras, 
are calculated mean, median and maximum of RAE values reached for each 
image. Subsequently, in figure \ref{fig:RAEstandard} the mean, median and maximum of the 
standard deviation obtained from each image, from each algorithm, are calculated 
again. As you can see, the GW algorithm is the only one to have the 
camera-independence for all the rooms used.

\begin{figure}[htbp]
    \centering
    \includegraphics[width = 1 \linewidth]{images/paper4/RAEHigh.png}
    \centering
    \caption{Recovery Angular Errors (Mean, Median and Maximum) of some algorithms.}
    \label{fig:RAE}
\end{figure}

\begin{figure}[htbp]
    \centering
    \includegraphics[width = 0.6 \linewidth]{images/paper4/standardHigh.png}
    \centering
    \caption{Mean, Median and Maximum RAE of some algorithms.}
    \label{fig:RAEstandard}
\end{figure}

\subsubsection{Evaluation of a Direct Supervised Method}
